Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
random edits

\begin{figure*}
\makebox[\textwidth][c]{
\begin{minipage}{0.6\textwidth}
  \begin{tabular}{lll}
    \toprule
    Name & Input & Output \\\midrule
    has-2 & [4\, 5\, 7\, 4] & \code{false} \\
    repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
    rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
    keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
    \bottomrule
  \end{tabular}
  \captionof{table}{Sample tasks from our list function domain}
  \label{listexamples}
\end{minipage}
\hfill
\begin{minipage}{0.6\textwidth}
  \centering
  \begin{tabular}{l}
    \toprule
    $f_0($\code{i$,\ell$}$) \,=\, $\code{(TODO)}\\
    \hspace{0.5cm}($f_0$: \emph{TODO})\\
  \bottomrule
  \end{tabular}
  \captionof{table}{Some learned DSL primitives for list functions}\label{listinduced}
\end{minipage}
  }
\end{figure*}

>>>>

\begin{comment}
\begin{table}
\centering
\begin{tabular}{lll}
  \toprule
  Name & Input & Output \\\midrule
  append-4 & [7\, 0\, 2] & [7\, 0\, 2\, 4] \\
  len & [3\, 5\, 12\, 1] & 4 \\
  has-2 & [4\, 5\, 7\, 4] & \code{false} \\
  repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
  drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
  count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
  rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
  pow-3 & [10\, 4\, 13] & [1000\, 64\, 2197] \\
  keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
  \bottomrule
\end{tabular}
\caption{Sample tasks from our list function domain %% We used 15 input/output
  %% examples for each task to reduce ambiguity in the task's function,
  %% ensuring solutions achieve the desired concept.
}
\label{listexamples}
\end{table}

\begin{table}[t]
  \centering
  \begin{tabular}{l}
    \toprule
    $f_0($\code{i$,\ell$}$) \,=\, $\code{(singleton (index i $\ell$))}\\
    \hspace{0.5cm}($f_0$: \emph{Put the $i$-th index into a list})\\
    $f_1($\code{i$,\ell$}$) \,=\, $\code{(++ $\ell$ ($f_0$ i $\ell$))}\\
    \hspace{0.5cm}($f_1$: \emph{Append the $i$-th index})\\
    $f_2($\code{n$,\ell$}$) \,=\, $\code{(any ($\lambda$ (x) (= n x)) $\ell$)}\\
    \hspace{0.5cm}($f_1$: \emph{Whether $n$ appears in the list})\\
    $f_3($\code{i$,\ell$}$) \,=\, $\code{(index (negate i) (sort $\ell$))}\\
    \hspace{0.5cm}($f_3$: \emph{Get the $i$-th largest number})\\
    $f_4($\code{n$,\ell$}$) \,=\, $\code{(mapi ($\lambda$ (i x) (mod x n)) $\ell$)}\\
    $f_5($\code{k$,\ell$}$) \,=\, $\code{(mapi ($\lambda$ (i x) (+ x k)) $\ell$)}\\
    $f_6($\code{k$,$n$,\ell$}$) \,=\, $\code{($f_4$ n ($f_5$ k $\ell$)}\\
    \hspace{0.5cm}($f_6$: \emph{Caesar shift of $k$ in integers modulo $n$})\\
  \bottomrule
  \end{tabular}
  \caption{Some learned DSL primitives for list functions}\label{listinduced}
\end{table}

  \end{comment}
